\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-23 k-planar.tex

\begin{table}
  \begin{center}
    \begin{tabular}{lccl}
      \textbf{Graph class} & \boldmath $\tw(H)$ & \boldmath $\ell$ & \textbf{Ref.} \\ \hline\hline
      Planar & $3^*$ & $3$ & \cite{DJMMUW20} \\
      Planar & $6^*$ & $1$ & \cite{UWY} \\
      Genus-$g$ & $3^*$ & $\max\{2g,3\}$ & \cite{DHHW} \\
      Genus-$g$ & $2g+6$ & 1 & \cite{UWY} \\
      Apex-minor-free & $O(1)$ & $O(1)$ & \cite{DJMMUW20} \\[1ex]
      % B-minor-free & $O(1)$ & $O(1)$ & \cite{DJMMUW20} \\
      $k$-planar & $\binom{k+4}{3}-1$ & $18k^2 + 48k + 30$ & \cref{kPlanarProduct} \\
      $(g,k)$-planar & $\binom{k+4}{3}-1$ & $\max\{2g,3\}(6k^2+16k+10)$ & \cref{gkPlanarProduct} \\
      $(g,\delta)$-string & $\binom{\delta+4}{3}-1$ & $\max\{2g,3\}(\delta^4 + 4\delta^3 + 9\delta^2 + 10\delta+4)$ & \cref{StringPartition} \\
      $k$-NN & $O(k^6)$ & $O(k^4)$ & \cref{nn_product_structure} \\
      $d$-framed & $3^*$ & $d+ 3\floor{d/2} - 3$ & \cref{d_framed_product_stucture} \\
      $1$-planar & $3^*$ & $7$ & \cref{1_planar_product} \\
      $d$-map & $3^*$ & $d+ 3\floor{d/2} - 3$ & \cref{NewMapGraph} \\
      $(g,d)$-map & $\textcolor{red}{?}$ & $\textcolor{red}{?}$ & \textcolor{red}{\cref{NewMapGraph}} \\ \hline
      \\[.2ex]
      \multicolumn{4}{l}{$^*$ the bound also applies to the simple treewidth of $H$.}
    \end{tabular}
  \end{center}
  \caption{Summary of known product structure theorems.}
  \label{summary_table}
\end{table}

@@

Since all the product structure theorems presented thus far upper bound the treewidth of $H$,
\cref{qn} immediately implies bounds on the queue number of all graphs in these classes.  An improvement can be made in the cases where $H$ is planar and has treewidth $3$, as follows.
\citet{ABGKP20} proved that every planar graph with treewidth at most $3$ has queue-number at most $5$. Thus the graph $H$ in \cref{1_planar_product} has queue-number at most $5$. \cref{qn,1_planar_product,NewMapGraph} then imply:

>>>>

\begin{table}
  \begin{center}
    \begin{tabular}{lccl}
      \textbf{Graph class} & \boldmath $\tw(H)$ & \boldmath $\ell$ & \textbf{Ref.} \\ \hline\hline
      Planar & $3^*$ & $3$ & \cite{DJMMUW20} \\
      Planar & $6^*$ & $1$ & \cite{UWY} \\
      Genus-$g$ & $3^*$ & $\max\{2g,3\}$ & \cite{DHHW} \\
      Genus-$g$ & $2g+6$ & 1 & \cite{UWY} \\
      Apex-minor-free & $O(1)$ & $O(1)$ & \cite{DJMMUW20} \\[1ex]
      % B-minor-free & $O(1)$ & $O(1)$ & \cite{DJMMUW20} \\
      $k$-planar & $\binom{k+4}{3}-1$ & $18k^2 + 48k + 30$ & \cref{kPlanarProduct} \\
      $(g,k)$-planar & $\binom{k+4}{3}-1$ & $\max\{2g,3\}(6k^2+16k+10)$ & \cref{gkPlanarProduct} \\
      $(g,\delta)$-string & $\binom{\delta+4}{3}-1$ & $\max\{2g,3\}(\delta^4 + 4\delta^3 + 9\delta^2 + 10\delta+4)$ & \cref{StringPartition} \\
      $k$-NN & $O(k^6)$ & $O(k^4)$ & \cref{nn_product_structure} \\
      $d$-framed & $3^*$ & $d+ 3\floor{d/2} - 3$ & \cref{d_framed_product_stucture} \\
      $1$-planar & $3^*$ & $7$ & \cref{1_planar_product} \\
      $d$-map & $3^*$ & $d+ 3\floor{d/2} - 3$ & \cref{dMapProduct} \\
      $(g,d)$-map & $\textcolor{red}{?}$ & $\textcolor{red}{?}$ & \textcolor{red}{\cref{dMapProduct}} \\ \hline
      \\[.2ex]
      \multicolumn{4}{l}{$^*$ the bound also applies to the simple treewidth of $H$.}
    \end{tabular}
  \end{center}
  \caption{Summary of known product structure theorems.}
  \label{summary_table}
\end{table}

@@

Since all the product structure theorems presented thus far upper bound the treewidth of $H$,
\cref{qn} immediately implies bounds on the queue number of all graphs in these classes.  An improvement can be made in the cases where $H$ is planar and has treewidth $3$, as follows.
\citet{ABGKP20} proved that every planar graph with treewidth at most $3$ has queue-number at most $5$. Thus the graph $H$ in \cref{1_planar_product} has queue-number at most $5$. \cref{qn,1_planar_product,dMapProduct} then imply:
